\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-26 paper.qmd
Updated single cell experiments section

In the field of single-cell studies, a common analytical task involves clustering to identify groups of cells with similar expression profiles. NLDR methods are commonly used to display clusters, and help to verify the results. For example, @chen2023 illustrates the use of UMAP to identify clusters in Human Peripheral Blood Mononuclear Cells (PBMC3k). @fig-umap-author is the reproduction of the published plot. It shows three well-separated clusters with big separations.

@@

As shown in @fig-tsne-suggest, there are three well-separated clusters, although the separation between the clusters are small. Additionally, non-linear structures can also be observed within the clusters (@fig-tsne-suggest). This demonstrates that tSNE accurately captures the data structure of the PBMC3k dataset, which UMAP did not achieve.

>>>>

In the field of single-cell studies, a common analytical task involves clustering to identify groups of cells with similar expression profiles. NLDR methods are commonly used to display clusters, and help to verify the results. For example, @chen2023 illustrates the use of UMAP to identify clusters in Human Peripheral Blood Mononuclear Cells (PBMC3k). @fig-NLDR-variety (a) is the reproduction of the published plot. It shows three well-separated clusters with big separations.

@@

As shown in @fig-NLDR-variety (e), there are three well-separated clusters, although the separation between the clusters are small. Additionally, non-linear structures can also be observed within the clusters (@fig-NLDR-variety (e)). This demonstrates that tSNE accurately captures the data structure of the PBMC3k dataset, which UMAP did not achieve.

### 2024-08-26 paper.tex
Updated single cell experiments section

In the field of single-cell studies, a common analytical task involves
clustering to identify groups of cells with similar expression profiles.
NLDR methods are commonly used to display clusters, and help to verify
the results. For example, \citet{chen2023} illustrates the use of UMAP
to identify clusters in Human Peripheral Blood Mononuclear Cells
(PBMC3k). \textbf{?@fig-umap-author} is the reproduction of the
published plot. It shows three well-separated clusters with big
separations.

@@

As shown in \textbf{?@fig-tsne-suggest}, there are three well-separated
clusters, although the separation between the clusters are small.
Additionally, non-linear structures can also be observed within the
clusters (\textbf{?@fig-tsne-suggest}). This demonstrates that tSNE
accurately captures the data structure of the PBMC3k dataset, which UMAP
did not achieve.

>>>>

In the field of single-cell studies, a common analytical task involves
clustering to identify groups of cells with similar expression profiles.
NLDR methods are commonly used to display clusters, and help to verify
the results. For example, \citet{chen2023} illustrates the use of UMAP
to identify clusters in Human Peripheral Blood Mononuclear Cells
(PBMC3k). Figure~\ref{fig-NLDR-variety} (a) is the reproduction of the
published plot. It shows three well-separated clusters with big
separations.

@@

As shown in Figure~\ref{fig-NLDR-variety} (e), there are three
well-separated clusters, although the separation between the clusters
are small. Additionally, non-linear structures can also be observed
within the clusters (Figure~\ref{fig-NLDR-variety} (e)). This
demonstrates that tSNE accurately captures the data structure of the
PBMC3k dataset, which UMAP did not achieve.
